\section{\textbf{Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Cadence Design Systems [\href{https://www.cadence.com/en_US/home.html}{\faIcon{globe}}]}{San Jose, CA}
{Application Engineer}{June 2024 - July 2025}
\resumeItemListStart
    \item Implemented multi-phase incremental compile strategies for \textbf{hardware-accelerated GPU emulation} flows, saving days of runtime.
    \item Integrated place \& route flow with proprietary client infrastructure.
    \item Completed bring-up projects to: remove consecutive inverters from a DSP with Cadence synthesis infrastructure; migrate RTL for a hardware compressor to Cadence verification infrastructure; verify sous-vide controller with UVM.
    \item Acquired \textbf{advanced industry training in digital design}, verification, implementation, \& EDA.
\resumeItemListEnd 

% \resumeSubheading
% {Eleos Technologies [\href{https://eleostech.com}{\faIcon{globe}}]}{Clemson, SC}
% {Software Tester}{January - April 2024}
% \resumeItemListStart
%     \item[] Verified software functionality and wrote reports on test failures.
% \resumeItemListEnd

\resumeSubheading
{Los Alamos National Lab [\href{https://www.lanl.gov}{\faIcon{globe}}]}{Los Alamos, NM (Remote)}
{Research Intern}{May - August 2022}
\resumeItemListStart
    \item Explored parallelization strategies for a novel data sampling algorithm.
    \item Optimized naive GPU kernels, yielding order-of-magnitude speedups for importance-based data sampling and \textbf{resulting in a published paper}.
    \item Contributed to \textbf{VizAly-Foresight, an open source compression benchmark} tool for domain scientists.
    \item \textbf{Presented results} at Clemson's Undergraduate Research Symposium.
\resumeItemListEnd

\resumeSubheading
{Clemson University FTHPC Lab [\href{https://jonccal.people.clemson.edu}{\faIcon{globe}}]}{Clemson, SC}
{NSF REU Student}{May - August 2021}
\resumeItemListStart
    \item Studied effects of lossy compression on statistical correlation analysis.
    \item Investigated ways to scale genomics workflows to heterogeneous clusters.
\resumeItemListEnd

\resumeSubheading
{Clemson University Watt Family Innovation Center [\href{https://www.clemson.edu/centers-institutes/watt/}{\faIcon{globe}}]}{Clemson, SC (Remote)}
{Research Intern}{May - August 2020}
\resumeItemListStart
    \item Hypothesized on statistical predictors of building energy usage.
    \item Compared efficiency vs quality-of-results tradeoffs of LSTM and ARIMA machine learning models for energy use forecasting.
    \item Trained \& deployed forecasting models to \textbf{run efficiently at scale} on heterogeneous compute systems.
\resumeItemListEnd

% \resumeSubheading
% {Greensboro Day School [\href{https://www.greensboroday.org}{\faIcon{globe}}]}{Greensboro, NC}
% {Technical Theater Assistant}{June - August, 2018 \& 2019}
% \resumeItemListStart
%     \item[] Assisted my high school's technical theater director in preparing for the following school year.
% \resumeItemListEnd

% \resumeSubheading
% {Moore Music Company [\href{https://www.mooremusiccompany.com}{\faIcon{globe}}]}{Greensboro, NC}
% {Instrument Repair Technician}{June - August, 2017}
% \resumeItemListStart
%     \item[] Repaired and cleaned band instruments to ready them for the following school year.
% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}
