\section{\textbf{Posters and Presentations}}
\vspace{-0.4mm}
\small{
\resumeSubHeadingListStart

\item \textbf{C. Sanders}, L. Durham, M. M. Martinez, D. Krasowska, E. Gindlesperger, B. Schlueter, J. C. Calhoun. (2022). \textbf{IndySCC 2022: Random Access Clemories}. \emph{International Conference for High Performance Computing, Networking, Storage and Analysis (SC22) Indy Student Cluster Competetion (IndySCC)}. \textbf{Best Poster}, IndySCC '22.

\item \textbf{C. Sanders}, J. C. Calhoun. (2022). \textbf{Parallelization Strategies for GPU Accelerated Data Sampling}. \emph{9th Annual Summer Undergraduate Research Symposium @ Clemson University}.

\item \textbf{C. Sanders}, S. Lam, A. Pendris, D. Krasowska, E. Gindlesperger, S. Ranjan. (2021). \textbf{SCC2021: Team Death Valley Computing}. \emph{International Conference for High Performance Computing, Networking, Storage and Analysis (SC21) Student Cluster Competetion (SCC)}.

% \item \textbf{C. Sanders}, J. C. Calhoun. (2021). \textbf{Effects of Lossy Compression on Correlation Workflows}.

\item \textbf{C. Sanders}, A. Abaunza, C. Ehrett, D. Herro, CC Bates. (2020). \textbf{Leveraging AI for Semi-Automatic Scoring of Running Records}. \emph{Watson-in-the-Watt AI Virtual Symposium @ Clemson University}.

\item \textbf{C. Sanders}. (2019). \textbf{But Can It Run Doom? Building a Breadboard Computer}. \emph{MakerDay 7 @ Clemson University.}

\item R. Catoe, E. Gindlesperger, A. Mahmood, T. Myers, \textbf{C. Sanders}, W. Smith. (2023). \textbf{Targeted Audio for Those Suffering Hearing Loss}. \emph{Clemson Spring 2023 ECE Senior Design Poster Session}.

\item T. Joseph, A. Garcia, S. Lam, W. Fey, D. Krasowska, E. Gindlesperger, B. Schlueter, C. Durham, \textbf{C. Sanders}, M. M. Herrera, J. C. Calhoun. (2023). \textbf{High-Performance Cluster Computing: Learning the Applications of Computing Methodologies in STEM Disciplines}. \emph{18th Annual Focus on Creative Inquiry (FoCI) Poster Forum @ Clemson University}.

\item C. Holt, G. Dube, S. Ranjan, \textbf{C. Sanders}, A. Bruner, W. Gossman, S. Placke, N. Heitzeg, J. Hollowell, J. C. Calhoun. (2021). \textbf{High-Performance Cluster Computing: Teaching Young Scientists and Engineers Future Computing Methodologies}. \emph{16th Annual Focus on Creative Inquiry (FoCI) Poster Forum @ Clemson University}.

\resumeSubHeadingListEnd
}
\vspace{-6mm}
