\section{\textbf{Undergraduate Research for Credit}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{High Performance Cluster Computing}
{PI: Assoc. Prof. Jon Calhoun}
{Two years; Five total credit hours}
{}
\resumeItemListStart
\item[] Competed at the 2021 and 2022 SC Student Cluster Competitions where my team won \textbf{Best Poster}, building mini clusters out of Raspberry Pi's and a real one out of Dell-sponsored hardware. Specialized in HPCG and CUDA, and \textbf{presented multiple years} at Clemson's Creative Inquiry Symposium.
\resumeItemListEnd

\resumeProject
{IBM Watson in the Watt}
{PI: Asst. Prof. Hudson Smith \& Dr. Carl Ehrett}
{One semester; Two total credit hours}
{}
\resumeItemListStart
\item[] Developed algorithms and frameworks to accelerate the scoring of literacy exams in elementary schools using speech-to-text services from IBM's Watson AI suite, and \textbf{presented results at Clemson's AI Symposium}.
\resumeItemListEnd

\resumeProject
{Machine Learning at Scale}
{PI: Assoc. Prof. Yuyuan "Lance" Ouyang}
{One year; Two total credit hours}
{}
\resumeItemListStart
\item[] Deployed reinforcement learning algorithms to an Nvidia DGX-2 AI Workstation to learn and play various arcade games.
\resumeItemListEnd

\resumeProject
{History of The Honors College}
{PI: Assoc. Prof. Joshua Catalano}
{One semester; One total credit hour}
{}
\resumeItemListStart
\item[] Investigated primary sources in Clemson's special collections archive and conducted oral history interviews to piece together the origins of Clemson University's Honors College.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}
